\documentclass{resume}

\usepackage[utf8]{inputenc}
\usepackage[left=0.4in,top=0.15in,right=0.4in,bottom=0.15in]{geometry}
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\renewcommand{\addressskip}{}
\renewcommand{\nameskip}{\smallskip}
\name{Vlad Temian}
\address{vladtemian@gmail.com \\ Timi\c{s}oara, Romania}
\phone{\href{https://github.com/vtemian}{github.com/vtemian} \\ \href{https://linkedin.com/in/vtemian}{linkedin/vtemian} \\ \href{https://blog.vtemian.com}{blog.vtemian.com}}

\begin{document}

\begin{center}
\em Founding engineer / CTO with agent-tooling depth. Ex-CTO, acquired by The Sandbox (Animoca Brands).\\
Shipping open-source agent dev tools; running Timi\c{s}oara's agentic dev community.
\end{center}
\smallskip

\begin{rSection}{Skills}
\textbf{Languages:} Python, TypeScript, Bash. \textbf{AI / Agents:} MCP, Claude API, OpenAI API, RAG, agent frameworks, prompt engineering and context management at scale. \textbf{Infra:} Kubernetes, Terraform, AWS, GCP, Cloudflare, Docker. \textbf{Data:} PostgreSQL, MySQL, ClickHouse, Redis. \textbf{Frontend / Mobile:} React, React Native, Next.js, Nuxt.js, NestJS.
\end{rSection}

\begin{rSection}{Experience}
    \begin{rSubsection}{The Sandbox (Animoca Brands), Principal Engineer}{2024 - Present}{}{}
        \begin{itemize}
            \setlength\itemsep{-0.4em}
            \item Built the AI-development practice from zero across a 15-engineer web squad: drove AI-generated code from 0\% to $\sim$95\% in 6 months. Owned the rollout end-to-end (internal talks, workflows, guardrails, agent skills, team setup)
            \item Streamlined releases from 5-7 people across 3 roles (QA, engineering, devops) per release down to 1 QA + 1 engineer on a weekly cadence
            \item Delivered 30-40\% cost reduction through infrastructure/tooling optimization and AI-driven replacements
            \item Set and shepherded engineering standards (code review, testing, branching, deploy); technical voice in product, infra and hiring decisions
        \end{itemize}
    \end{rSubsection}
    \begin{rSubsection}{QED, Co-founder \& CTO}{09/2020 - 2024}{}{}
        \item \href{https://qed.builders}{Venture studio} that bootstrapped and scaled startups. \textbf{Acquired by The Sandbox (Animoca Brands)}
        \begin{itemize}
            \setlength\itemsep{-0.4em}
            \item Scaled engineering 0 $\rightarrow$ 24 across portfolio companies; per company, owned stack, architecture and team-shape calls
            \item \textbf{Lektrico} (EV charging): built React Native iOS/Android app from zero, designed AWS/Terraform infra, wrote microservices for OTA firmware updates and MQTT IoT comms. Now ships $\sim$2,000 chargers/year across RO, IT, FR
            \item Other portfolio work: Knowledgecoop (mortgage LMS, MySQL $\rightarrow$ PostgreSQL zero-downtime migration; Next.js + Hasura, ClickHouse analytics), HeyLady (NestJS LMS, 120+ countries), Tagarer (MLOps), Hypereal (real-time RAG)
        \end{itemize}
    \end{rSubsection}
    \begin{rSubsection}{Presslabs}{10/2013 - 04/2018, 03/2019 - 09/2020}{}{}
        \item Open-source WordPress hosting on Kubernetes operators
        \begin{itemize}
            \setlength\itemsep{-0.4em}
            \item Created \href{https://github.com/presslabs/gitfs}{Gitfs} (2.6K\textsuperscript{+} stars on GitHub), a FUSE filesystem on Git for SFTP. Ran 500-600 production mounts per server in production at Presslabs
            \item Led team of 4 on the client dashboard (Python/Django/K8s); integrated payment gateways and bridged Kubernetes with legacy infra (Go)
        \end{itemize}
    \end{rSubsection}
    \begin{rSubsection}{Gorgias}{04/2018 - 03/2019}{}{}
        \item Customer support automation for e-commerce (YC alum, React + Python/Flask/PostgreSQL)
        \begin{itemize}
            \setlength\itemsep{-0.4em}
            \item Shipped revenue-attribution feature linking CS agent recommendations to upsell revenue; built automated K8s staging provisioning from scratch
        \end{itemize}
    \end{rSubsection}
\end{rSection}

\begin{rSection}{Selected Projects}
    \begin{itemize}
        \setlength\itemsep{-0.3em}
        \item \textbf{\href{https://www.npmjs.com/package/micode}{micode} + \href{https://github.com/vtemian/octto}{octto}} (670\textsuperscript{+} GitHub stars combined, $\sim$1.8K monthly npm installs): OpenCode plugin suite. micode adds a structured Brainstorm $\rightarrow$ Plan $\rightarrow$ Implement workflow with session continuity; octto turns terminal agent flows into an interactive browser UI for AI brainstorming
        \item \textbf{\href{https://claudebin.com}{claudebin}}: share and resume Claude Code sessions via a single URL, with embeddable iframes. \href{https://news.ycombinator.com/item?id=47073488}{Show HN}, growing daily
        \item Also building: \textbf{\href{https://github.com/vtemian/zag}{zag}} (agent dev env in Zig), \textbf{\href{https://www.npmjs.com/package/@agentprobe/core}{agentprobe}} (passive observability for coding agents, 4 providers), \textbf{\href{https://opnble.dev}{opnble}} (one-click run-any-repo desktop), \textbf{\href{https://cursouls.xyz}{cursouls}}. Earlier: \href{https://github.com/vtemian/django-server-timing}{django-server-timing}, \href{https://github.com/vtemian/buffpy}{buffpy}, \href{https://github.com/presslabs/zipa}{zipa}
    \end{itemize}
\end{rSection}

\begin{rSection}{Community}
    \begin{itemize}
       \setlength\itemsep{-0.3em}
       \item Co-founder, organizer and speaker, \textbf{agentic.tm} (Timi\c{s}oara agentic dev community). Co-organizer: RoPython TM, Algorithms Meetup, Hack\&Tell, Code4Romania. Jury, \href{https://infoeducatie.ro}{Infoeducatie} National CS Contest
    \end{itemize}
\end{rSection}

\begin{rSection}{Education}
\item \textbf{B.S. Computer Science}, West University of Timi\c{s}oara, Faculty of Computer Science and Mathematics \hfill 2013 - 2016
\end{rSection}

\end{document}
